\section{Data Description}\label{sec: description}
The dataset (originally in excel format) that we are using for our report was downloaded from Kaggle.com, an online platform for predictive modeling and analytics  competitions in which companies, researchers post data and statisticians along with data miners compete to produce the best models for predicting and describing the data. (link to the dataset = https://www.kaggle.com/samdeeplearning/real-estate-vermont-newhampshire) \\

The dataset uploaded to Kaggle was collected from real observations  from the website MLS.com, which stands for "Multiple Listings Service", and it is America's number one Real Estate Portal.\\

We use ideas and concepts from several publications, such as JuanPablo Murillos publication about analysis of home sales in King County, and another publication from Greg Merell. He also worked with King's County data, and used multiple regression techniques, which we will introduce and adjust for our report. Both of the projects were published on the rpubs website, where data scientists and statisticians publish their works and analyses done with the R programming language.\\

The observations took place in two states in the U.S., Vermont and New Hampshire, which are two neighbouring states located on the north-east coast. Vermont and New Hampshire have a population density of 26.1/$km^2$ and 56.8/$km^2$, respectively. Our dataset contains 6019 observations of 21 variables. The original dataset contained 46 variables, but we deleted the ones not relevant for our analysis. The dataset contains real estate listings in the time frame from the beginning of 2012 until mid 2017. \\

The variables used in the dataset are described in the List of Abbreviations section.  
After describing the dataset, we move forward to explain the adjustments made to the dataset.\\

