

\section{Results and Limitations}\label{Sec:Results}



While analysing the dataset of the house prices in Vermont and New Hamphire, we wanted to answer research questions like which variable has the strongest influence on the price or how does the age of the building affect the price of a property. \\
As stated several times, the size of a property has the strongest influence on the price. The bigger a property is, the higher the price. On average the house price increases by 0.68\% according to our Model 3 for 1\% Increase in SqFt. And also the age of a house has an significant effect on the price sold. When the house gets 1\% older, the price decreases slightly. \\
We could have gone into a more detailed analysis, taking for example the real estate agencies, tax assesments and other variables into account. The problem is with these, that they are not true parameters for a real estate, and they don?t really describe one either. The variables that we used, however, are the fundamentals of a house or a condominium, and can accurately describe a property. \\

Using the correlation calculations, and the visualized correlation matrix proved our assumptions made in the beginning of the paper. The strongest correlation effect is between the logsqft and the number of rooms: the more bedrooms a house has, the larger the size of it will be. We also have high effects when looking at the number of bathrooms, or the number of bedrooms. The logprice has high correlation with bedrooms and rooms in total. More importantly, the logprice correlates mostly with the logsqft. To answer our question we asked at the beginning: from a statistical point of view, it is true that the bigger a house is, the more it would cost. Of course, we only observed 2 states in the U.S., which means that we should not get into any general conclusions that can apply to any other state or country, but we assume that the theory we proved here is consistent in other countries in the world as well. However, proving this assumption could be a part of further project by analysing more real estate data from other countries with our compiled regression model.\\
